Scikit-learn: machine learning without learning the machinery

### 2014-07-01 article.tex
in, not on, a figure

On Fig.\,\ref{fig:random_forest}, we use a popular machine-learning
algorithm, random forests, to predict the wage from the years of
education, or the years of work experience, either as separate features,
or combined. The patchy square appearance of the prediction is due to the
inners of the algorithm, and it illustrates the corresponding
extrapolation mechanism. The predictions fit the data well; maybe too
well, as, on the prediction solely from the years of education (left of
the figure), it is hard to believe in the bump at 5 years. This bump is
probably a classic case of \emph{overfit}: the algorithm is learning its
prediction from noise in the data. As a result, the prediction error on
new data will be significantly different than that measured on the
training data.

@@

On Fig.\,\ref{fig:linear_svm}, we use another popular machine-learning
algorithm, linear Support Vector Machines (SVMs). Unlike random forests,
it learns decisions with linear functions. It is said that
it has a lower \emph{model complexity}, because the number of parameters
to learn from the data is much smaller. The risk here is to
\emph{underfit}: not fully use the richness of the data, that may not be
following a linear law. The art of machine learning consists in choosing
the right family of algorithms (or models) to describe the data well and
find the sweet spot between under and over fit. As the number of features
describing the data grows, the number of parameters to learn grows, and
thus the risk of overfit increases. This core difficulty is known as the
\emph{curse of dimensionality}.

@@

On Fig.\,\ref{fig:code} we give an example of fully functioning code to
do sentiment polarity classification for movie reviews: given a review,
it outputs whether the review is positive about the movie it concerns.
The code demonstrates the use of pipelines, and also shows how machine
learning ties into unrelated Python's modules: downloading, unpacking and
learning from a dataset are all done in one programming language.
This script first fetches a hand-labeled movie review dataset
\cite{pang2004} and unpacks it to disk using standard Python libraries.
It then loads these using scikit-learn data loading functions, makes a
pipeline of a \textsf{tf--idf} feature extractor
\cite{rennie2003tackling} --that turns strings into a sparse matrix based
on word frequencies-- and logistic regression, and finally trains the
model. Parameters for the feature extractor and the classifier
were set manually.

>>>>

In Fig.~\ref{fig:random_forest}, we use a popular machine-learning
algorithm, random forests, to predict the wage from the years of
education, or the years of work experience, either as separate features,
or combined. The patchy square appearance of the prediction is due to the
inners of the algorithm, and it illustrates the corresponding
extrapolation mechanism. The predictions fit the data well; maybe too
well, as, on the prediction solely from the years of education (left of
the figure), it is hard to believe in the bump at 5 years. This bump is
probably a classic case of \emph{overfit}: the algorithm is learning its
prediction from noise in the data. As a result, the prediction error on
new data will be significantly different than that measured on the
training data.

@@

In Fig.~\ref{fig:linear_svm}, we use another popular machine-learning
algorithm, linear Support Vector Machines (SVMs). Unlike random forests,
it learns decisions with linear functions. It is said that
it has a lower \emph{model complexity}, because the number of parameters
to learn from the data is much smaller. The risk here is to
\emph{underfit}: not fully use the richness of the data, that may not be
following a linear law. The art of machine learning consists in choosing
the right family of algorithms (or models) to describe the data well and
find the sweet spot between under and over fit. As the number of features
describing the data grows, the number of parameters to learn grows, and
thus the risk of overfit increases. This core difficulty is known as the
\emph{curse of dimensionality}.

@@

In Fig.~\ref{fig:code} we give an example of fully functioning code to
do sentiment polarity classification for movie reviews: given a review,
it outputs whether the review is positive about the movie it concerns.
The code demonstrates the use of pipelines, and also shows how machine
learning ties into unrelated Python's modules: downloading, unpacking and
learning from a dataset are all done in one programming language.
This script first fetches a hand-labeled movie review dataset
\cite{pang2004} and unpacks it to disk using standard Python libraries.
It then loads these using scikit-learn data loading functions, makes a
pipeline of a \textsf{tf--idf} feature extractor
\cite{rennie2003tackling} --that turns strings into a sparse matrix based
on word frequencies-- and logistic regression, and finally trains the
model. Parameters for the feature extractor and the classifier
were set manually.
